Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-03 WSSSPE1_report/WSSSPE1_summary_report.tex
removing sentence in abstract

Unique perspectives were captured about issues such as comprehensive
documentation, development and deployment practices, software
licenses and career paths for developers. Attribution systems that accounts for 
evidence of software contribution and impact were also discussed. These include
mechanisms such as Digital Object Identifiers, publication
of ``software papers'', and the use of online systems, for example source code repositories
like GitHub. For truly sustainable software, there should be no
end, as the software products will continue to be used beyond a single
institution, grant, and developer or development team.

>>>>

Unique perspectives were captured about issues such as comprehensive
documentation, development and deployment practices, software
licenses and career paths for developers. Attribution systems that account for 
evidence of software contribution and impact were also discussed. These include
mechanisms such as Digital Object Identifiers, publication
of ``software papers'', and the use of online systems, for example source code repositories
like GitHub. %For truly sustainable software, there should be no
%end, as the software products will continue to be used beyond a single
%institution, grant, and developer or development team.
